An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-07 ex3/paper/paper.tex
Addresse Max' comment

\subsection{Evaluation}
% \begin{figure*}
% \includegraphics[width=0.45\textwidth]{adv_plots/cwl1.pdf}
% \includegraphics[width=0.45\textwidth]{adv_plots/cwl2.pdf}
% \caption{Performance of the \gls{cw} with different $\epsilon$ values for $\ell_1$ and $\ell_2$ distances.}
% \label{fig:adv_cw}
% \end{figure*}
\todo{Max: Fix me. Don't know how the reference became invalid...}
\autoref{fig:adv_cw} depicts the ratio of attack flows which were successfully misclassified as benign with respect to the final packet along with the resulting distance from the original sample. Evidently, the larger the $\epsilon$ parameter, the better the attack works, but also the distances become larger.

@@

% \begin{figure*}
% \includegraphics[width=0.45\textwidth]{adv_plots/fgsm.pdf}
% \includegraphics[width=0.45\textwidth]{adv_plots/l_inf_pgd.pdf}
% \caption{Performance of FSGM and $\ell_\infty$-bounded \gls{pgd} for different bounds.}
% \label{fig:fgsm}
% \end{figure*}

@@

Furthermore, let $f_A(x)$  denote the joint probability \todo{Max: Ist joint probability nicht immer wenn man mehrere Ereignisse hat? Ich hätte hier probability density function geschrieben...} for classification as attack with a feature value $x$. Accuracy then is $\int f_A(x) dx$ for attacks and $1-\int f_A(x) dx$ for benign traffic. \autoref{fig:mutinfo_example} shows two different distributions
yielding the same accuracy, but clearly the right-side distribution has a larger influence on the prediction, as in the right-side case the prediction deterministically depends on the feature value.
To capture such dependencies, we propose to use mutual information instead of accuracy drop to determine feature sensitivity.
Mutual Information between two random variables $X,Y$ is defined as 
\begin{equation}
I_{X,Y} = \mathbb E \left\{ \log\left(\frac{f_{X,Y}(x,y)}{f_X(x)f_Y(y)}\right) \right\},
\end{equation}
with $f_X(x), f_Y(y)$ and $f_{X,Y}(x,y)$ denoting the distribution of $X,Y$ and their joint distribution, respectively. To obtain feature sensitivity, we compute mutual information between an input variable and the prediction output for one flow at one particular time step, and average over the result for the test dataset.

>>>>

\subsection{Evaluation}
\begin{figure*}
\includegraphics[width=0.45\textwidth]{adv_plots/cwl1.pdf}
\includegraphics[width=0.45\textwidth]{adv_plots/cwl2.pdf}
\caption{Performance of the \gls{cw} with different $\epsilon$ values for $\ell_1$ and $\ell_2$ distances.}
\label{fig:adv_cw}
\end{figure*}
\todo{compress figures somehow}
\autoref{fig:adv_cw} depicts the ratio of attack flows which were successfully misclassified as benign with respect to the final packet along with the resulting distance from the original sample. Evidently, the larger the $\epsilon$ parameter, the better the attack works, but also the distances become larger.

@@

\begin{figure*}
\includegraphics[width=0.45\textwidth]{adv_plots/fgsm.pdf}
\includegraphics[width=0.45\textwidth]{adv_plots/l_inf_pgd.pdf}
\caption{Performance of FSGM and $\ell_\infty$-bounded \gls{pgd} for different bounds.}
\label{fig:fgsm}
\end{figure*}

@@

Furthermore, let $f(A,x)$  denote the joint probability
%\todo{Max: Ist joint probability nicht immer wenn man mehrere Ereignisse hat? Ich hätte hier probability density function geschrieben...}
%AH. changed notation and wording
for classification as attack and a feature value $x$. Accuracy then is $\int f(A,x) dx$ for attacks and $1-\int f(A,x) dx$ for benign traffic.
\autoref{fig:mutinfo_example} shows two different distributions
yielding the same accuracy, but clearly the right-side distribution has a larger influence on the prediction, as in the right-side case the prediction deterministically depends on the feature value.
To capture such dependencies, we propose to use mutual information instead of accuracy drop to determine feature sensitivity.
Mutual Information between two random variables $X,Y$ is defined as 
\begin{equation}
I_{X,Y} = \mathbb E \left\{ \log\left(\frac{f_{X,Y}(x,y)}{f_X(x)f_Y(y)}\right) \right\},
\end{equation}
with $f_X(x), f_Y(y)$ and $f_{X,Y}(x,y)$ denoting the distribution of $X,Y$ and their joint distribution, respectively. To obtain feature sensitivity, we compute mutual information between an input variable and the prediction output for one flow at one particular time step, and average over the result for the test dataset.
